Clinical prediction using similarity-based cohorts: A scoping review

### 2023-04-03 docs/Manuscript/Manuscript.Rmd
revise manuscript per outstanding prisma items

  We searched five electronic bibliographic databases for publications that report applications of localized models to tasks involving analysis of clinical or health data. Two authors divided title/abstract screening and collaboratively reviewed screened entries for inclusion. We also reviewed a seed set that inspired the review and traced a subset of citations from  We discussed and summarized settings, tasks, and tools; identified and tabulated themes; and synthesized the methods into a general framework.

@@

We include a PRISMA checklist as Supplemental Table 1.
Because we focus on methodologies rather than approaches, we deviate in some ways from PRISMA guidelines. In particular, many items of the checklist, involving bias assessment and quantitative synthesis, are intended for meta-analyses and, therefore, did not apply to this study.

@@

## Title/Abstract screen

@@

>>>>

  We searched four electronic bibliographic platforms (PubMed, Web of Science, Academic Search Premier, and MathSciNet) during 2021 July 19–22. We screened and reviewed entries based on four criteria intended to specify applications of localized models to tasks involving analysis of clinical or health data. Two authors divided title/abstract screening and collaboratively reviewed screened entries for inclusion. We also screened and reviewed a seed set that inspired the review and traced methodological citations from included entries. We discussed and summarized settings, tasks, and tools; identified and tabulated themes; and synthesized the methods into a general framework. We received no specific funding for this work.

@@

We include a PRISMA checklist as Supplemental Table 1.
Because we focus on methodologies rather than approaches, we deviate in some ways from PRISMA guidelines. In particular, many items of the checklist, involving bias assessment and quantitative synthesis, are intended for meta-analyses and, therefore, did not apply to this study.
Because we are not aware of any standard procedures for conducting reviews and syntheses of methodology, no protocol was prepared for this study.

@@

## Title/abstract screen

@@

# Acknowledgments

# Support

The authors received no specific funding or other support for this work.

# Competing interests

The authors declare that they have no competing interests.

# Data and code availability

Data collected or encoded for included studies are publicly available in two Google Sheets. Code used to analyze these data and generate this manuscript is publicly available in a GitHub repository.

* Properties of included studies: <https://docs.google.com/spreadsheets/d/1tpWMhYH2pyRT55K7n2J2XFs-kEV_JTuCDmXzJ4BBgNo/>
* Composite techniques: <https://docs.google.com/spreadsheets/d/1xvDJwiLBoI2oz8fxHJ5MjNmiju_RAlK7RJv-wXe1DAs/>
* Analysis and manuscript code: <https://github.com/corybrunson/imsr>
